### 2014-07-27 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Report: Minor edit
Chicago: minor edit to report

\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~(\ref{fig:simp_geom}).
\begin{table}
\centering
\captionof{table}{Abridged NISOH approximate fire event timeline}\label{tab:fire_info}
\begin{tabular}{cl}
\toprule[1.5pt]
Incident Time  &  Fire Behavior / Fireground Operation  \\
(hh:mm:ss)     &                                        \\
\midrule
\multirow{2}{*}{17:15:00} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
         & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
         & \\[.25cm]
\multirow{2}{*}{17:20:00}    & \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
         & \\[.25cm] 
17:21:00 & E123 captain and firefighter on 2nd floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
17:21:30 & 1st floor exterior porch door opened. \\[.25cm]
\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
         & \\[.25cm]
17:24:00    & Water applied to attic from the rear exterior position. \\[.25cm]
17:25:00    & SQ5 makes entry through front of structure. \\[.25cm]
17:27:00    & After hearing a Mayday call from SQ5, IC calls a Mayday. \\[.25cm]
17:29:00    & E123 captain carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

While we had to estimate the time at which the door failed, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created. This resulted in a rapid change in the conditions within the flow path. The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate. The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
\caption[Dimensioned drawing of 1st floor.]{Dimensioned drawing of 1st floor. The measurements are accurate to within 15 cm (6 in).}
\label{fig:first_floor}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
\caption[Dimensioned drawing of 2nd floor.]{Dimensioned drawing of 2nd floor. The measurements are accurate to within 15 cm (6 in).}
\label{fig:second_floor}
\end{figure}

>>>>

\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~(\ref{fig:simp_geom}).
\begin{table}
\centering
\captionof{table}{Abridged NISOH approximate fire event timeline}\label{tab:fire_info}
\begin{tabular}{cl}
\toprule[1.5pt]
Incident Time  &  Fire Behavior / Fireground Operation  \\
{[hh:mm:ss]}   &                                        \\
\midrule
\multirow{2}{*}{17:15:00} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
         & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
         & \\[.25cm]
\multirow{2}{*}{17:20:00}    & \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
         & \\[.25cm] 
17:21:00 & E123 captain and firefighter on 2nd floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
17:21:30 & 1st floor exterior porch door opened. \\[.25cm]
\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
         & \\[.25cm]
17:24:00    & Water applied to attic from the rear exterior position. \\[.25cm]
17:25:00    & SQ5 makes entry through front of structure. \\[.25cm]
17:27:00    & After hearing a Mayday call from SQ5, IC calls a Mayday. \\[.25cm]
17:29:00    & E123 captain carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

While the food failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created. This resulted in a rapid change in the conditions within the flow path. The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate. The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
\caption[Dimensioned drawing of 1st floor.]{Dimensioned drawing of 1st floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:first_floor}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
\caption[Dimensioned drawing of 2nd floor.]{Dimensioned drawing of 2nd floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:second_floor}
\end{figure}
